---
title: "Alcohol vs Seat choice"
author: "Brooke De La Torre"
date: "10/15/20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??   
$_H0$:There is no difference in the average mean alcohol consumption based on seating location   
$_Ha$:There is a difference in the average mean alcohol consumption based on seating location    
    

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P value is 0.00011 < 0.05 so we reject the null hypothesis
```{r}
plot(TukeyHSD(model1))
```

## Conclusions

There is a difference in the alcohol consumption based on the seat you choose to sit, Alcohol was mostly consumed by people sitting in the back, we would reject the null hypothesis because the p-value is less than 0.05. Alcohol does influence seating arrangement.