---
title: "Alcohol vs Seat choice"
author: "Brooke De La Torre"
date: "10/15/20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??   
$_H0$:There is no difference in the average mean alcohol consumption based on seating location   
$_Ha$:There is a difference in the average mean alcohol consumption based on seating location    
    

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P value is 0.00011 < 0.05 so we reject the null hypothesis
```{r}
plot(TukeyHSD(model1))
```

## Conclusions
There is a difference between alcohol consumption and seating from front-back, there is a difference in consumption from middle-back, There is no difference in consumption and seating for middle-front.

There is no correlation between seating arrangement and alcohol consumption when it comes to middle-front. there is a correlation when seating is front-back and middle-back.
